Geometric Control for Autonomous Landing on Asteroids

### 2017-08-10 manuscript.tex
Remove todo list
Add motion estimate to paper

% TODO: detail on nonlinear controller
\begin{itemize}
    \item Show development of \SE controller
    \item Summarize the stability proof for trajectory tracking
    \item We're assuming a fully actuated spacecraft
\end{itemize}

@@

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
\begin{figure}[htbp]
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_mappoints.png} 
        \caption{ORB-SLAM2 Feature Tracking Visualization\label{fig:orbslam_mappoints}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_localization.png} 
        \caption{ORB-SLAM2 Localization from monocular images \label{fig:orbslam_localization}} 
    \end{subfigure} 
\end{figure}
% TODO: Plots of trajectory

% TODO: Control input plot
% TODO: Show estimation from SLAM
\section{Conclusions}\label{sec:conclusions}
There have been a variety of approaches for the analysis and design of orbital trajectories around asteroids.
Relatively less work has been directed towards the design of landing trajectories.
Furthermore, much of the previous work has only treated the orbital or translational dynamics.
The approximation of a spacecraft as a point mass rather than an extended rigid body severely limits the applicability and ignores a major component of the dynamic environment.
This work directly derives the equations of motion of a dumbbell spacecraft around an asteroid described using a polyhedron potential model. 
We explicitly consider the impact of the gravitational moment on both the orbit and attitude dynamics. 
With this accurate equations of motion we develop geometric nonlinear controllers which allow for the vehicle to track a desired landing trajectory. 
The landing portion allows for an end to end mission design scheme based on rigorous geometric mechanics techniques.

>>>>

@@

Concurrent with the simulation, we generate images of Itokawa using Blender, as described earlier.
The images are generated at a rate of \SI{1}{\hertz} and stored for post processing and one exampel view is shown in~\cref{fig:example_image}. 
From these images we estimate the position of the camera relative to the asteroid using monocular localization.
In this work, we demonstrate the ability to generate realistic imagery and the processing of these images to determine a state estimate of the camera pose.
In future work, we seek to use this state estimate in a closed-loop controller to enable a fully-autonomous control system for the spacecraft. 
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/test000837.png}
    \caption{Example image of Itokawa at \( t = \SI{837}{\second}\)\label{fig:example_image}}
\end{figure}
From each image, a series of features are detected and tracked between subsequent frames.
A visualization of this process is shown in~\cref{fig:orbslam_mappoints} which shows the tracked features of the image in green.
From these tracked features it is possible to estimate the relative motion of the camera~\cite{szeliski2010}.
\Cref{fig:orbslam_localization} shows a visualization of the localization process from the imagery. 
Through monocular images it is not possible to compute the position of the camera relative to the inertial frame.
Rather, it is only possible to determine a camera pose accurate to an unknown scale factor. 
This limitation is intrinsic to the transformation of the three-dimensional scene onto the two-dimensional image plane~\cite{szeliski2010}.
However, it is possible to compute the relative motion between sequential images and we use this to estimate the motion of the camera.
\begin{figure}[htbp]
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_mappoints.png} 
        \caption{ORB-SLAM2 Feature Tracking Visualization\label{fig:orbslam_mappoints}} 
    \end{subfigure}~
    \begin{subfigure}[htbp]{0.5\textwidth} 
        \includegraphics[width=\textwidth, keepaspectratio]{figures/orbslam_localization.png} 
        \caption{ORB-SLAM2 Localization from monocular images \label{fig:orbslam_localization}} 
    \end{subfigure} 
\end{figure}

An additional complexity is due to the fact that the dynamic equations of motion are defined in the inertial reference frame. 
As a result, the asteroid is rotating relative to this frame while the dumbbell is moving relative to the inertial frame. 
The majority of SLAM methodologies use the implicit assumption of a stationary scene or terrain and a moving camera. 
As a result, the motion estimate from the imagery is defined relative to the asteroid fixed frame, rather than the inertial frame. 
However, we assume that the motion of the asteroid is known and constant. 
Over the relatively short timespan of the simulation this is an appropriate assumption and does not significantly affect the solution.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/keyframe_estimate.pdf}
    \caption{Comparison of image estimate and true trajectory in asteroid fixed frame\label{fig:estimate}}
\end{figure}
\Cref{fig:estimate} shows a comparison of the estimated position in blue and the true position in the asteroid fixed frame. 
The estimate is quite accurate in the \( x \) axis. 
This is primarily due to the fact that during the vertical descent that asteroid remains fixed relative to the spacecraft. 
As a result, a large number of image features are able to be accurately tracked during the motion towards the surface. 
This is also evident by the denser keyframes in the later portion of the simulation as compared to the beginning. 
The estimate tends to diverge in the other two axes.
However, the general trend is captured in the \( y \) axis and the error in the \( z \) axis is on the order of \SI{100}{\meter}. 
This simulation demonstrates the ability to track a desired trajectory for the coupled motion of a rigid spacecraft on \SE.
Furthermore, we show the ability to estimate the motion using a single monocular camera during a short duration landing trajectory. 
In spite of the complex and difficult lighting conditions an estimate is able to be generated.

\section{Conclusions}\label{sec:conclusions}
There have been a variety of approaches for the analysis and design of orbital trajectories around asteroids.
Relatively less work has been directed towards the design of landing trajectories.
Furthermore, much of the previous work has only treated the orbital or translational dynamics.
The approximation of a spacecraft as a point mass rather than an extended rigid body severely limits the applicability and ignores a major component of the dynamic environment.
This work directly derives the equations of motion of a dumbbell spacecraft around an asteroid described using a polyhedron potential model. 
We explicitly consider the impact of the gravitational moment on both the orbit and attitude dynamics. 
With this accurate equations of motion we develop geometric nonlinear controllers which allow for the vehicle to track a desired landing trajectory. 
The landing portion allows for an end to end mission design scheme based on rigorous geometric mechanics techniques.
